\textcolor{Navy}{\textsc{Convexity adjustments with a bit of Malliavin}}

### 2022-11-01 Latex/paper.tex
Adding Description Section 4
Adding Description Section 4

\section{Convexity Adjustment}\label{sec:CA}
$\cdots$  tengo que pensar que poner aqui como intro

>>>>

\section{Convexity Adjustment}\label{sec:CA}
In this section, we derive the convexity adjustment for different products. The advantage of using the Malliavin calculus is that it allows us to derive a convexity adjustment directly for a general model. 
Since this convexity adjustment works for a general framework defined in the Cheyette model, it can be applied to all included models, such as the Hull-White model.
